Increase of GDP and Monetary Expansion

### 2023-02-22 outputs/paper/paper.qmd
Final Revision
Final Revision with updated abstract and github link

---
title: Increase of GDP and Monetary Expansion
subtitle: An Analysis of Potential Factors from 16th to 19th century
author: 
  - Rae Zhang
  - Jenny Shen
  - Sarah Zhang
thanks: "Code, data and reproduction package are available at: https://github.com/JunweiZhang130/Replication-for-The-real-effects-of-monetary-expansions-evidence-from-a-large-scale-history.git and https://www.socialsciencereproduction.org/reproductions/8d4a8d6c-9f9f-44dc-bd97-9c810ed677f6/index "
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper discusses the causal relationship between GDP growth and monetary expansion from the 16th to the 19th century, with the intent to identify the potential factors that contributed to economic growth during this period. Using a historical analysis approach, the paper examines multiple datasets including the nominal and real GDP of different European countries, the production of precious metals in the Americas, and the mint output of England that gave a glimpse to what potentially stimulates economic growth. The findings suggest that monetary injection played a significant role in increasing mint output and driving GDP growth during this period. Additionally, the study highlights the importance of monetary policies in promoting economic development. Overall, this paper provides insights into the factors that drove economic growth during a critical period in economic history. "
format: pdf
output: bookdown::pdf-document2
bibliography: references.bib
---

@@

## The Real and Nominal GDP over the Period of 1500 to 1800

@@

>>>>

---
title: Increase of GDP and Monetary Expansion
subtitle: An Analysis of Potential Factors from 16th to 19th century
author: 
  - Rae Zhang
  - Jenny Shen
  - Sarah Zhang
thanks: "Code and data available at: https://github.com/JunweiZhang130/Replication-for-The-real-effects-of-monetary-expansions-evidence-from-a-large-scale-history.git ; A replication of various Aspects in this paper are available at:  https://doi.org/10.48152/ssrp-6nfn-1g27"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: |
  \section*{\centering \abstractname}
  This paper discusses the causal relationship between GDP growth and monetary expansion from the 16th to the 19th century, with the intent to identify the potential factors that contributed to economic growth during this period. Using a historical analysis approach, the paper examines multiple datasets including the nominal and real GDP of different European countries, the production of precious metals in the Americas, and the mint output of England that gave a glimpse to what potentially stimulates economic growth. The findings suggest that monetary injection played a significant role in increasing mint output and driving GDP growth during this period. Additionally, the study highlights the importance of monetary policies in promoting economic development. Overall, this paper provides insights into the factors that drove economic growth during a critical period in economic history.
format: pdf
bibliography: references.bib
---

@@

## 3.1 The Real and Nominal GDP Trends

@@

\newpage
## 3.2 Share of Gold in Total Production
